Appendix B: Examples of Deep RL in Ecological Decision Problems

### 2021-06-04 appendices/appendix-B-examples.Rmd
typo

# Create a fishing environment
# Create an agent
ppo_tuned = sb3$PPO("MlpPolicy",
                    "env" = vec_env, 
                    "seed" = seed,
                    "batch_size" = 64L,
                    "n_steps" = 32L,
                    "gamma" = 0.9999,
                    "learning_rate" = 0.00037996229760279524,
                    "ent_coef" = 2.392750198613048e-08,
                    "clip_range" = 0.3,
                    "n_epochs" = 10L,
                    "gae_lambda" = 0.92,
                    "max_grad_norm" = 0.7,
                    "vf_coef" = 0.4863551514846155,
                    "policy_kwargs" = list(
                      "net_arch" = c(64L, 64L),
                      "activation_fn" = torch$nn$ReLU
                     )
                   )

@@

  # RL-recommended harvest action:
  out = agent$predict(state, determinstic=TRUE)
  action = out[[1]]

>>>>

# Create a fishing environment
# Create an agent
ppo_tuned = sb3$PPO("MlpPolicy",
                    "env" = vec_env, 
                    "seed" = seed,
                    "batch_size" = 64L,
                    "n_steps" = 32L,
                    "gamma" = 0.9999,
                    "learning_rate" = 0.00037996229760279524,
                    "ent_coef" = 2.392750198613048e-08,
                    "clip_range" = 0.3,
                    "n_epochs" = 10L,
                    "gae_lambda" = 0.92,
                    "max_grad_norm" = 0.7,
                    "vf_coef" = 0.4863551514846155,
                    "use_sde" = TRUE,
                    "policy_kwargs" = list(
                      "net_arch" = list(list(pi=c(64L, 64L), vf=c(64L, 64L))),
                      "activation_fn" = torch$nn$ReLU
                     )
                   )

@@

  # RL-recommended harvest action:
  out = agent$predict(state, deterministic = TRUE)
  action = out[[1]]
